---
title: Primer post desde el addin
author: EK
date: '2019-05-28'
slug: primer-post-desde-el-addin
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2019-05-28T15:54:48-07:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---


Un poco de Rmarkdown para ver que pasa

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::knit_hooks$set(error = function(x, options) {
  paste0("<pre style=\"color: red;\"><code>", x, "</code></pre>")
})
```

To understand how R works, you are going to use it as a simple calcuator.
You can get output in the Console simply by typing math in the script and running it:
```{r three-plus-five, echo=TRUE}
3+5 # From the pound sign to the right, this is a comment. I am asking R to sum 3 plus 5
```
  
Now, we divide 12 by 6 and write a comment explaining what we are doing
```{r calculator-ex-solution}
12/6 # I am now dividing 12 by 6. The solution is 2
```


# 1.Basics R

## First steps
To write a comment, type `#` before the sentence you want to write.
Anything to the right of a `#` in a script will be ignored by R.
To run any line (or lines), click anywhere on the line you want to run and either 1) click `Ctr` + `Enter` or 2) click on the run bottom (up right corner of Source/Script in Rstudio)
<div id="print-weight-hint">
**Hint:** If you want to run several lines, highlight them all and do as explained above.
</div>  